Embedding Dimension of Polyhedral Losses

### 2020-06-09 colt-20/embed-dim-submission.tex
Fixing \cite to \citet or \citep

% \paragraph{Properties of distributions.}
In order to study calibration of surrogates (Definition~\ref{def:calibration} below), it is useful to formalize the following functions that describe the reports that minimize expected $\ell$-loss and $L$-loss under $p$.
%% Bo: since we use \gamma and \R for \ell, and we use \Gamma and \reals^d for L,
%% I figured generic properties could use notation g and R for f
\begin{definition}[(Finite) property, level set, elicited]\jessiet{Bo in FIXME: Change $\R$ since this is the only place $\R$ is not finite?}\jessiet{Changed $\R$ to $\R'$?}
  A \emph{property} is a function $\Gamma: \simplex \to 2^{\R'}$ for some set $\R'$ where $\Gamma(p) \neq \emptyset$ for all $p$.
  It is \emph{finite} if $|\R'| < \infty$.
  The \emph{level set} of $r \in \R'$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
  A loss function $L: \R' \to \nonnegreals^{\Y}$ \emph{elicits} $\Gamma$ if $\Gamma(p) = \argmin_{r \in \R'} \inprod{p}{L(r)}$.
\end{definition}
In this paper we write $\ell$ for discrete losses (i.e., when $|\R|$ is finite), and $\gamma$ instead of $\Gamma$ for the property elicited by $\ell$, reserving $\Gamma$ and $L$ for properties and losses on report space $\R=\reals^d$.
For example, 0-1 loss elicits the mode, which is formalized as a property on report space $\R = \Y$ via $\gamma(p) = \argmax_{y \in \Y} p_y$.
Notice in this example $\gamma(p)$ is a singleton set when the mode of $p$ is unique and e.g. is $\Y$ when $p$ is uniform.
%Another example of a finite property is ranking, in which $\R$ is the set of permutations of $\Y$, and $g(p)$ consists of all permutations that order $\Y$ from most to least probable (i.e. ties must be broken in all possible ways).

@@

%\jessie{Not a smooth transition here...} \bo{I think it's ok...}
%Polyhedral surrogates are motivated by the following results.
\begin{theorem}[\cite{finocchiaro2019embedding}] \label{thm:embed-iff-poly}
  Given a discrete loss $\ell$, (1) there exists a polyhedral loss $L$ embedding $\ell$; and (2) there exists a link function calibrating $L$ to $\ell$.
\end{theorem}
In other words, polyhedral surrogates are equivalent to embeddings of discrete losses $\ell$ in $\reals^d$, and they come with a guarantee of calibration.
This raises the question studied in this paper: for a given discrete loss, in what dimension $d$ does such a surrogate exist?
This question is captured by the following quantity.

@@

In general (e.g. \cite{finocchiaro2019embedding}\jessiet{Change citation probably.  Possibly to \cite[Corollary 13]{ramaswamy2016convex}}), a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $d = n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
Lower bounds exist but are rare.
A lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates.
\cite{ramaswamy2016convex} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g. prove that embedding 0-1 loss on $n$ labels requires dimension $n-1$.
However, this technique gives only the trivial $d \geq 1$ for the abstain family of losses above when $\alpha \leq 1/2$ because of their geometric structure.
We discuss further in \S~\ref{sec:conclusion}.

@@

\begin{definition}[Intersection graph]\label{def:intersection-graph}
  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \to 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$\jessiet{Is it this or add an edge if $\gamma_r \cap \gamma_{r'}$ is full dimensional in the simplex?}, where $\relint(\simplex)$ is the relative interior of $\simplex$.
  %(distributions with full support).
\end{definition}

@@

\begin{proposition} \label{prop:orderable-iff-path}
  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph\jessiet{tree?} where every vertex has either one or two neighbors.\jessiet{Bo in FIXME: ``Proposition 10: why is the incorrect 'definition' of path still there?'' I don't see why this is wrong?}
\end{proposition}

@@

\jessiet{Promised to give reviewers more intuition for this $\Lambda$ notation}
\begin{theorem} \label{thm:construct-1d-loss}
  Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss.
  Then $\ell$ is $1$-embeddable if and only if there is an ordering $\R = \{r_1,\ldots,r_k\}$ of the reports such that the following two conditions hold, where $v(i)_y := \ell(r_i)_y - \ell(r_{i-1})_y$:
  \begin{enumerate}
  \item For all $y\in\Y$, the sequence $\sgn(v(i)_y)$ is monotone in
    $i\in\{1,\ldots,k-1\}$,
  \item For all $i\in\{2,\ldots,k-1\}$
    \begin{align*}
      \lambda^-(i) &= \min \left\{\frac{v(i)_y}{v({i+1})_y} : y\in\Y, v(i)_y, v({i+1})_y < 0\right\}
      \\
      \lambda^+(i) &= \max \left\{\frac{v(i)_y}{v({i+1})_y} : y\in\Y, v(i)_y, v({i+1})_y > 0\right\}~,
    \end{align*}
    we have $\lambda^-(i) \geq \lambda^+(i)$.
    (We adopt the convention $\max(\emptyset) = -\infty$, $\min(\emptyset) = +\infty$.)
  \end{enumerate}

@@

We summarize the above results in the following theorem, together with one additional result, whose proof is in Appendix~\ref{app:1-dim}: if $\ell$ has any calibrated convex surrogate at all, it must have a polyhedral one.
(See Conjecture~\ref{conj:embed-equals-ccdim} regarding higher dimensional generalizations.)
\begin{theorem} \label{thm:1d-tfae}
  Let $\ell$ be a discrete loss eliciting a finite property $\gamma$.
  The following are equivalent: (1) $\gamma$ is orderable; (2) the intersection graph of $\gamma$ is a path; (3) the two conditions of Theorem \ref{thm:construct-1d-loss} are satisfied; (4) $\ell$ is $1$-embeddable; (5) $\ell$ has some polyhedral calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$; (6) $\ell$ has some convex calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$.
\end{theorem}
\jessiet{If I understand correctly, different orderings of the reports may yield different embeddings, and these different embeddings should elicit different properties.  How to we reconcile this in the theorem statement?  Or where am I wrong?}

@@

Our characterization of 1-embeddable losses reveals a large class of properties are not $1$-embeddable.
% On the other hand, previous work has shown that every discrete loss is $(n-1)$-embeddable
% \citep{finocchiaro2019embedding}.
% A natural next question, therefore, is to characterize $d$-embeddable losses for $2 \leq d \leq n-2$, or failing that, to develop tighter bounds on the embedding dimension of various losses.
In this section, we develop a characterization of $d$-embeddable discrete losses for $d \geq 2$.
We begin with some basic facts and definitions about polytopes and their Minkowski sums, which naturally arise when considering the subgradients of a polyhedral surrogate loss (\S~\ref{subsec:sub-sets}).
From these definitions, we can state a somewhat immediate characterization of $d$-embeddable losses in terms of polytopes that satisfy certain optimality and monotonicity conditions (\S~\ref{subsec:gener-char}, Theorem~\ref{thm:general-char}).
We then explore the optimality condition further, and through facts about Minkowski sums, slowly remove mentions of polytopes from the condition until we arrive at a quadratic feasibility program to test whether such polytopes exist (\S~\ref{subsec:opt-conditions}, Theorem~\ref{thm:opt-iff-qfp}).
% Finally, we discuss the proof of correctness of our feasibility program together with intuition.
From our main characterization, dropping the monotonicity condition, this program gives a novel necessary condition for $d$-embeddability, yielding new lower bounds for embedding dimension (Corollary~\ref{cor:d-embeddable-char}).

@@

Recall that if $\ell: \R \to \nonnegreals^{\Y}$ is embedded by $L: \reals^d \to \nonnegreals^{\Y}$, then each $r \in \R$ is embedded at some point $\varphi(r) \in \reals^d$.
In particular, $\varphi(r)$ must minimize $\inprod{p}{L(\cdot)}$ if and only if $r$ minimizes $\inprod{p}{\ell(\cdot)}$.
The key to our approach is to study as first-class objects the sets of all subgradients\footnote{Recall that a subgradient of e.g. the convex function $L(\cdot)_y: \reals^d \to \reals$ at a point $u$ is a vector $v \in \reals^d$ such that $L(u')_y \geq L(u)_y + \inprod{v}{u'-u}$ for all $u'$.} of $L$ at these embedding points.
The question of whether a calibrated polyhedral surrogate exists in $d$ dimensions essentially reduces to conditions on these sets alone.
\raft{The ``essentially'' is because we need loss values to match.  It's not clear if that comes for free, i.e., if you embed the correct property, can you always modify the loss to match $\ell$?}
In particular, we use the fact that a convex function is minimized at $u$ if and only if $\vec{0}$ is in its subgradient set at $u$.
\jessiet{Promised more intuition on $\T$ vs $\T^r$.}
Therefore, we consider collections of sets $T^r_y$, which intuitively aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $\varphi(r)$, denoted $\partial L(\varphi(r))_y$.
Throughout, we often take $r$ as implicit and suppress it from our notation for ease of exposition.
Note that if $L(\cdot)_y$ is a polyhedral function on $\reals^d$, then all of its subgradient sets are (bounded) closed polytopes~\citep{rockafellar1997convex}.

@@

Note that $\T = \T^r$ for some $r \in \R$; here, $r$ is understood, so we omit it for clarity.
The importance of the $p$-weighted Minkowski sum and of $D(\T)$ are that they capture the distributions $p$ for which a point $u$ minimizes expected loss, whenever $\T$ corresponds to the subgradient sets of some polyhedral $L$ at $u$.
In other words, under these conditions, we have $D(\T) = \Gamma_u$, the level set for $u$ of the property $\Gamma$ elicited by $L$.
\begin{lemma} \label{lem:minkowski-0-opt}
  Let $L: \reals^d \to \nonnegreals^{\Y}$ be a polyhedral loss eliciting a property $\Gamma$.
  If for all $y\in\Y$ we have $T_y = \partial L(u)_y$ at some point $u\in\reals^d$, then $D(\T) = \Gamma_u$.
\end{lemma}
\begin{proof}
  Recall that a convex function $f$ is minimized at $u = \varphi(r)$ if and only if $\vec 0 \in \partial f(u)$.
  % Let $f(u) = \inprod{p}{L(u)}$.
  We thus have $p\in\Gamma_u \iff u \in \argmin_{u'} \inprod{p}{L(u')} \iff \vec 0 \in \partial\inprod{p}{L(u)} = \mathop{\bigoplus}_{y\in\Y} p_y \partial L(u)_y = \oplus_p \T \iff p\in D(\T)$.
  Here we used the basic fact that if $f_1,f_2$ are convex with subgradient sets $T_1,T_2$ at $u$, then $\alpha f_1 + \beta f_2$ has subgradient set $\alpha T_1 \oplus \beta T_2$, the Minkowski sum of the scaled sets.
  % So $\vec 0$ is a subgradient of $\inprod{p}{L(\varphi(r))}$ if and only if $\vec 0 \in \oplus_p \T$, which by definition occurs if and only if $p \in D(\T)$.
\end{proof}
This fact will be vital for characterizing when $\ell$ is correctly embedded by some $L$ whose subgradient sets are $\T^r$ for each $r \in \R$.

@@

The two conditions above give us a much better understanding of when a given set of polytopes $\T$ satisfies the optimality condition, and the proof of Theorem~\ref{thm:vertex-halfspace-opt} is shown in Appendix~\ref{app:omitted-d-dim}.
We are still left with the problem, however, of understanding when such a set $\T$ exists.
Intuitively, the biggest hurdle that remains is the quantification over sets of polytopes, a massive search space.
Surprisingly, one can reduce this search to a quadratic feasibility program, which we now give.
The key insight involves the halfspace condition, and observing that given a certain ``complete'' set of normal vectors, one can exactly describe the support function of $\oplus_p\T$ in terms of the support functions of each $T_y$ and each normal vector $v$.
From here, we use the fact that this description is linear in $p$, and can therefore relate it directly to the given matrix $B$.

@@

Essentially the only other known lower-bound technique for dimensionality of calibrated surrogates is the \emph{feasible subspace dimension} of \cite{ramaswamy2016convex}.
This crux of this technique is also an optimality condition on a surrogate loss, showing that if $\vec 0$ is in the $p$-weighted Minkowski sum of the subgradient sets of $L$, then there is some local affine set of dimension $n-d-1$ such that $\vec 0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the set, and thus the set must be contained in $\gamma_r$.
% This implies the flat must be contained in every level set $\gamma_r$ that $p$ is in.
Therefore, for example, if the intersection of several level sets is a single vertex $v$ (as in e.g. 0-1 loss for the uniform distribution), then the only such set can be of dimension $0$, which gives a $d \geq n-1$ lower bound.

@@

  Let $\gamma:\simplex\to 2^\R \setminus \{\emptyset\}$ be finite and orderable.
  From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : \inprod{v_1}{p} \leq 0\}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
  From the positive orientation of the $v_i$, we have for all $p\in\simplex$ that $\sgn(\inprod{v_i}{p})$ is monotone in $i$.
  In particular, it must be that for all $y$, $\sgn((v_i)_y)$ is monotone in $i$, taking the distribution with all weight on outcome $y$, thus establishing the first condition.
  % (Similarly, if $\gamma(\ones_y) = \{r_j,r_{j+1}\}$, then $(v_i)_y = v_i \cdot \ones_y < 0$ for $i < j$, $(v_j)_y = 0$, and $(v_i)_y > 0$ for $i > j$.)
  % \raft{This observation could use a better proof.}

@@

  Let $\gamma:\simplex\to 2^\R \setminus \{\emptyset\}$ be finite and monotone.
  Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{a(r_{i+1})}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$.
  If this intersection is empty, then there must be some $p$ with $\inprod{b(r_i)}{p} < 0$ and $\inprod{a(r_{i+1})}{p} > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
  Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
\end{proof}

@@

\jessiet{This seems like it should be a corollary of Theorem 12 now by observing that indirect elicitation implies calibrated surrogate.}
\newcommand{\Pbar}{\overline P}
\begin{proposition}\label{prop:indirect-orderable}
  If convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
\end{proposition}
\begin{proof}
  Let $\gamma:\simplex\to 2^\R \setminus \{\emptyset\}$.
  From Lemma~\ref{lem:prop-L-monotone} below, $\Gamma := \prop{L}$ is monotone.
  Let $\psi:\reals\to\R$ be the calibrated link from $\Gamma$ to $\gamma$.
  From Lemma~\ref{lem:pbar}, we have $\Pbar_r = \gamma_r$ for all $r\in\R$, where $\Pbar_r$ is the closure of the convex hull of $\bigcup_{u\in\psi^{-1}(r)} \Gamma_u$.

@@

\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\to 2^\reals \setminus \{\emptyset\}$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.  Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
\begin{lemma}\label{lem:prop-L-monotone}
  For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
\end{lemma}
\begin{proof}
  If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
  We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
  The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
  % Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
\end{proof}

>>>>

% \paragraph{Properties of distributions.}
In order to study calibration of surrogates (Definition~\ref{def:calibration} below), it is useful to formalize the following functions that describe the reports that minimize expected $\ell$-loss and $L$-loss under $p$.
%% Bo: since we use \gamma and \R for \ell, and we use \Gamma and \reals^d for L,
%% I figured generic properties could use notation g and R for f
\begin{definition}[(Finite) property, level set, elicited]
  A \emph{property} is a function $\Gamma: \simplex \to 2^{\R}$ for some set $\R$ where $\Gamma(p) \neq \emptyset$ for all $p$.
  It is \emph{finite} if $|\R| < \infty$.
  The \emph{level set} of $r \in R$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
  A loss function $L: \R \to \nonnegreals^{\Y}$ \emph{elicits} $\Gamma$ if $\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}$.
\end{definition}
In this paper we write $\ell$ for discrete losses (i.e., when $|\R|$ is finite), and $\gamma$ instead of $\Gamma$ for the property elicited by $\ell$, reserving $\Gamma$ and $L$ for properties and losses on report space $\R=\reals^d$.
For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $\R = \Y$ via $\gamma(p) = \argmax_{y \in \Y} p_y$.
Notice in this example $\gamma(p)$ is a singleton set when the mode of $p$ is unique and e.g. is $\Y$ when $p$ is uniform.
%Another example of a finite property is ranking, in which $\R$ is the set of permutations of $\Y$, and $g(p)$ consists of all permutations that order $\Y$ from most to least probable (i.e. ties must be broken in all possible ways).

@@

%\jessie{Not a smooth transition here...} \bo{I think it's ok...}
%Polyhedral surrogates are motivated by the following results.
\begin{theorem}[\cite{finocchiaro2019embedding}] \label{thm:embed-iff-poly}
  If a discrete loss $\ell$ is embedded by some surrogate $L$, then (1) $L$ must be a polyhedral loss; and (2) there exists a link function calibrating $L$ to $\ell$.
\end{theorem}
In other words, polyhedral surrogates are equivalent to embeddings of discrete losses $\ell$ in $\reals^d$, and they come with a guarantee of calibration.
This raises the question studied in this paper: for a given discrete loss, in what dimension $d$ does such a surrogate exist?
This question is captured by the following quantity.

@@

In general (e.g. \cite{finocchiaro2019embedding}\jessiet{Change citation probably.  Possibly to \cite[Corollary 13]{ramaswamy2016convex}}), a known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $d = n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.
Lower bounds exist but are rare.
A lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates.
\cite{ramaswamy2016convex} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g. prove that embedding $0-1$ loss on $n$ labels requires dimension $n-1$.
However, this technique gives only the trivial $d \geq 1$ for the abstain family of losses above when $\alpha \leq 1/2$ because of their geometric structure.
We discuss further in \S~\ref{sec:conclusion}.

@@

\begin{definition}[Intersection graph]\label{def:intersection-graph}
  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \toto 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$\jessiet{Is it this or add an edge if $\gamma_r \cap \gamma_{r'}$ is full dimensional in the simplex?}, where $\relint(\simplex)$ is the relative interior of $\simplex$.
  %(distributions with full support).
\end{definition}

@@

\begin{proposition} \label{prop:orderable-iff-path}
  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph\jessiet{tree?} where every vertex has either one or two neighbors.
\end{proposition}

@@

\begin{theorem} \label{thm:construct-1d-loss}
  Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss.
  Then $\ell$ is $1$-embeddable if and only if there is an ordering $\R = \{r_1,\ldots,r_k\}$ of the reports such that the following two conditions hold, where $v(i)_y := \ell(r_i)_y - \ell(r_{i-1})_y$:
  \begin{enumerate}
  \item For all $y\in\Y$, the sequence $\sgn(v(i)_y)$ is monotone in
    $i\in\{1,\ldots,k-1\}$,
  \item For all $i\in\{2,\ldots,k-1\}$
    \begin{align*}
      \lambda^-(i) &= \min \left\{\frac{v(i)_y}{v({i+1})_y} : y\in\Y, v(i)_y, v({i+1})_y < 0\right\}
      \\
      \lambda^+(i) &= \max \left\{\frac{v(i)_y}{v({i+1})_y} : y\in\Y, v(i)_y, v({i+1})_y > 0\right\}~,
    \end{align*}
    we have $\lambda^-(i) \geq \lambda^+(i)$.
    (We adopt the convention $\max(\emptyset) = -\infty$, $\min(\emptyset) = +\infty$.)
  \end{enumerate}

@@

We summarize the above results in the following theorem, together with one additional result: if $\ell$ has any calibrated convex surrogate at all, it must have a polyhedral one.
(See Conjecture~\ref{conj:embed-equals-ccdim} regarding higher dimensional generalizations.)
\begin{theorem} \label{thm:1d-tfae}
  Let $\ell$ be a discrete loss eliciting a finite property $\gamma$.
  The following are equivalent: (1) $\gamma$ is orderable; (2) the intersection graph of $\gamma$ is a path; (3) the two conditions of Theorem \ref{thm:construct-1d-loss} are satisfied; (4) $\ell$ is $1$-embeddable; (5) $\ell$ has some polyhedral calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$; (6) $\ell$ has some convex calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$.
\end{theorem}
\jessiet{If I understand correctly, different orderings of the reports may yield different embeddings, and these different embeddings should elicit different properties.  How to we reconcile this in the theorem statement?  Or where am I wrong?}

@@

Our characterization of 1-embeddable losses reveals a large class of properties are not $1$-embeddable.
% On the other hand, previous work has shown that every discrete loss is $(n-1)$-embeddable
% \citep{finocchiaro2019embedding}.
% A natural next question, therefore, is to characterize $d$-embeddable losses for $2 \leq d \leq n-2$, or failing that, to develop tighter bounds on the embedding dimension of various losses.
In this section, we develop a characterization of $d$-embeddable discrete losses for $d \geq 2$.
We begin with some basic facts and definitions about polytopes and their Minkowski sums, which naturally arise when considering the subgradients of a polyhedral surrogate loss (\S~\ref{subsec:sub-sets}).
From these definitions, we can state a somewhat immediate characterization of $d$-embeddable losses in terms of polytopes that satisfy certain optimality and monotonicity conditions (\S~\ref{subsec:gener-char}).
We then explore the optimality condition further, and through facts about Minkowski sums, slowly remove mentions of polytopes from the condition until we arrive at a quadratic feasibility program to test whether such polytopes exist (\S~\ref{subsec:opt-conditions}).
% Finally, we discuss the proof of correctness of our feasibility program together with intuition.
From our main characterization, dropping the monotonicity condition, this program gives a novel necessary condition for $d$-embeddability, yielding new lower bounds for embedding dimension (Corollary~\ref{cor:d-embeddable-char}).

@@

Recall that if $\ell: \R \to \nonnegreals^{\Y}$ is embedded by $L: \reals^d \to \nonnegreals^{\Y}$, then each $r \in \R$ is embedded at some point $\varphi(r) \in \reals^d$.
In particular, $\varphi(r)$ must minimize $\inprod{p}{L(\cdot)}$ if and only if $r$ minimizes $\inprod{p}{\ell(\cdot)}$.
The key to our approach is to study as first-class objects the sets of all subgradients\footnote{Recall that a subgradient of e.g. the convex function $L(\cdot)_y: \reals^d \to \reals$ at a point $u$ is a vector $v \in \reals^d$ such that $L(u')_y \geq L(u)_y + \inprod{v}{u'-u}$ for all $u'$.} of $L$ at these embedding points.
The question of whether a calibrated polyhedral surrogate exists in $d$ dimensions essentially reduces to conditions on these sets alone.
\raft{The ``essentially'' is because we need loss values to match.  It's not clear if that comes for free, i.e., if you embed the correct property, can you always modify the loss to match $\ell$?}
In particular, we use the fact that a convex function is minimized at $u$ if and only if $\vec{0}$ is in its subgradient set at $u$.

Therefore, we consider collections of sets $T^r_y$, which intuitively aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $\varphi(r)$, denoted $\partial L(\varphi(r))_y$.
Throughout, we often take $r$ as implicit and suppress it from our notation for ease of exposition.
Note that if $L(\cdot)_y$ is a polyhedral function on $\reals^d$, then all of its subgradient sets are (bounded) closed polytopes~\citep{rockafellar1997convex}.

@@

The importance of the $p$-weighted Minkowski sum and of $D(\T)$ are that they capture the distributions $p$ for which a point $u$ minimizes expected loss, whenever $\T$ corresponds to the subgradient sets of some polyhedral $L$ at $u$.
In other words, under these conditions, we have $D(\T) = \Gamma_u$, the level set for $u$ of the property $\Gamma$ elicited by $L$.
\begin{lemma} \label{lem:minkowski-0-opt}
  Let $L: \reals^d \to \nonnegreals^{\Y}$ be a polyhedral loss eliciting a property $\Gamma$.
  If for all $y\in\Y$ we have $T_y = \partial L(u)_y$ at some point $u\in\reals^d$, then $D(\T) = \Gamma_u$.
\end{lemma}
\begin{proof}
  Recall that a convex function $f$ is minimized at $u$ if and only if $\vec 0 \in \partial f(u)$.
  % Let $f(u) = \inprod{p}{L(u)}$.
  We thus have $p\in\Gamma_u \iff u \in \argmin_{u'} \inprod{p}{L(u')} \iff \vec 0 \in \partial\inprod{p}{L(u)} = \mathop{\bigoplus}_{y\in\Y} p_y \partial L(u)_y = \oplus_p \T \iff p\in D(\T)$.
  Here we used the basic fact that if $f_1,f_2$ are convex with subgradient sets $T_1,T_2$ at $u$, then $\alpha f_1 + \beta f_2$ has subgradient set $\alpha T_1 \oplus \beta T_2$, the Minkowski sum of the scaled sets.
  % So $\vec 0$ is a subgradient of $\inprod{p}{L(\varphi(r))}$ if and only if $\vec 0 \in \oplus_p \T$, which by definition occurs if and only if $p \in D(\T)$.
\end{proof}
This fact will be vital for characterizing when $\ell$ is correctly embedded by some $L$ whose subgradient sets are $\T^r$ for each $r \in \R$.

@@

The two conditions above give us a much better understanding of when a given set of polytopes $\T$ satisfies the optimality condition.
We are still left with the problem, however, of understanding when such a set $\T$ exists.
Intuitively, the biggest hurdle that remains is the quantification over sets of polytopes, a massive search space.
Surprisingly, one can reduce this search to a quadratic feasibility program, which we now give.
The key insight involves the halfspace condition, and observing that given a certain ``complete'' set of normal vectors, one can exactly describe the support function of $\oplus_p\T$ in terms of the support functions of each $T_y$ and each normal vector $v$.
From here, we use the fact that this description is linear in $p$, and can therefore relate it directly to the given matrix $B$.

@@

Essentially the only other known lower-bound technique for dimensionality of calibrated surrogates is the \emph{feasible subspace dimension} of \cite{ramaswamy2016convex}.
This crux of this technique is also an optimality condition on a surrogate loss, showing that if $\vec 0$ is in the $p$-weighted Minkowski sum of the subgradient sets of $L$, then there is some local affine set of dimension $n-d-1$ such that $\vec 0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the set, and thus the set must be contained in $\gamma_r$.
% This implies the flat must be contained in every level set $\gamma_r$ that $p$ is in.
Therefore, for example, if the intersection of several level sets is a single vertex $v$ (as in e.g. $0-1$ loss for the uniform distribution), then the only such set can be of dimension $0$, which gives a $d \geq n-1$ lower bound.

@@

  Let $\gamma:\simplex\toto\R$ be finite and orderable.
  From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : \inprod{v_1}{p} \leq 0\}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
  From the positive orientation of the $v_i$, we have for all $p\in\simplex$ that $\sgn(\inprod{v_i}{p})$ is monotone in $i$.
  In particular, it must be that for all $y$, $\sgn((v_i)_y)$ is monotone in $i$, taking the distribution with all weight on outcome $y$, thus establishing the first condition.
  % (Similarly, if $\gamma(\ones_y) = \{r_j,r_{j+1}\}$, then $(v_i)_y = v_i \cdot \ones_y < 0$ for $i < j$, $(v_j)_y = 0$, and $(v_i)_y > 0$ for $i > j$.)
  % \raft{This observation could use a better proof.}

@@

  Let $\gamma:\simplex\toto\R$ be finite and monotone.
  Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{a(r_{i+1})}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$.
  If this intersection is empty, then there must be some $p$ with $\inprod{b(r_i)}{p} < 0$ and $\inprod{a(r_{i+1})}{p} > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
  Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
\end{proof}

@@

\jessiet{This seems like it should be a corollary of Theorem 12 now by observing that indirect elicitation implies calibrated surrogate.}
\newcommand{\Pbar}{\overline P}
\begin{proposition}\label{prop:indirect-orderable}
  If convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
\end{proposition}
\begin{proof}
  Let $\gamma:\simplex\toto\R$.
  From Lemma~\ref{lem:prop-L-monotone} below, $\Gamma := \prop{L}$ is monotone.
  Let $\psi:\reals\to\R$ be the calibrated link from $\Gamma$ to $\gamma$.
  From Lemma~\ref{lem:pbar}, we have $\Pbar_r = \gamma_r$ for all $r\in\R$, where $\Pbar_r$ is the closure of the convex hull of $\bigcup_{u\in\psi^{-1}(r)} \Gamma_u$.

@@

\raft{The following statement is true I believe, but low priority: ``An elicitable property $\Gamma:\simplex\toto\reals$ is convex elicitable (elicited by a convex $L : \reals \to \reals^\Y$) if and only if it is monotone.''  Start of the proof commented out.  Just need to show that $b$ is the upper limit of $a$ and $a$ the lower of $b$; should follow from elicitability of $\Gamma$.}
\begin{lemma}\label{lem:prop-L-monotone}
  For any convex $L : \reals \to \reals^\Y_+$, the property $\prop{L}$ is monotone.
\end{lemma}
\begin{proof}
  If $L$ is convex and elicits $\Gamma$, let $a,b$ be defined by $a(r)_y = \partial_- L(r)_y$ and $b(r) = \partial_+ L(r)_y$, that is, the left and right derivatives of $L(\cdot)_y$ at $r$, respectively.
  Then $\partial L(r)_y = [a(r)_y,b(r)_y]$.
  We now have $r \in \prop{L}(p) \iff 0 \in \partial \inprod{p}{L(r)} \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$, showing the first condition.
  The second condition follows as the subgradients of $L$ are monotone functions (see e.g.~\citet[Theorem 24.1]{rockafellar1997convex}).
  % Conversely, given such an $a,b$, we appeal to~\citet[Theorem 24.2]{rockafellar1997convex}, which gives us that $L(u)_y := \int_0^u a(u)_y$ is convex, and
\end{proof}
